\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-02-26 papers/itsc_2012/draft2.tex
gridlock 99% fixed for stop signs and traffic lights! (using a generalized lookahead engine and judicious cancelation of signal waiting)
agents creep forward properly to fix a close-intersection, unsynced-light issue
no more ugly notion of 'yielding' lock to a stop sign, now that creep-forward behavior works.

\commentd{describe traffic signal policy, once it's working fully}

@@

>>>>

\commentd{describe traffic signal policy, once it's working fully. the delay
thing is maybe interesting.}

@@

\commentd{this is now fixed in most cases. describe, and describe a better
  workaround for some cases: S turns}
\commentd{and describe the full-capacity case and how that's hopeless anyway}
